---
title: "Validate Input"
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

<!-- One line about what the function does -->

`validate_arguments` decorator allows the arguments passed to a function to be
parsed and validated using the function's annotations before the function is
called.

## How It Works

`validate_arguments` provides an extremely easy way to apply validation to your
code with minimal boilerplate. The original function needs to have key-value
pairs in its declaration, where the each value carries its designated class.

## When to Use It

* To protect functions from receiving unexpected types of input arguments. 
* In [`ValueObjects`](https://tidylab.github.io/R6P/reference/ValueObject.html). 

## Examples: Functions with Built-in NA classes

Given a `Customer` [`ValueObject`](https://tidylab.github.io/R6P/reference/ValueObject.html)

```{r, echo=TRUE}
Customer <- function(given = NA_character_, family = NA_character_)
    return(data.frame(given = given, family = family))
```

When `Customer` is decorated with `validate_arguments`

```{r, echo=TRUE}
Customer <- validate_arguments(Customer)
```

Then passing arguments of any type other then the declared type prompts an informative error.

In the `Customer` example, both input arguments `given` and `family` are declared as `character`. 

```{r, echo=TRUE}
Customer(given = "Bilbo", family = "Baggins") # Works as both arguments are character
try(Customer(given = "Bilbo", family = 90201)) # Fails because family is not a character
```
