---
title: "Decorator Underlying Mechanism"
bibliography: [../../inst/REFERENCES.bib]
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

## Prerequisites

Decorators use:

* [Functions as objects](https://adv-r.hadley.nz/functions.html#first-class-functions)
* Functions as return values
* [Lexical scoping](https://adv-r.hadley.nz/functions.html#lexical-scoping)
* [Closures](https://adv-r.hadley.nz/environments.html#function-environments)

To fully understand decorators underlying mechanism, you should be familiar
these topics.

## How does a decorator look like?

```{r, echo=TRUE}
decorator_skeleton <- function(func){
    # Define a new function that perform additional functionality before/after 
    # calling the original function
    wrapper <- function(...){
        # (optional) Do something before
        NULL
        # Call the original function
        result <- func(...)
        # (optional) Do something after
        NULL
        # Return result
        return(result)
    }
    
    return(wrapper)
}
```

Finally, we apply the decorator to a function (i.e. decorating) with

```{r, echo=TRUE, eval=TRUE}
sum <- decorator_skeleton(base::sum)
class(sum)
```

## Step-by-step example

In this example, we create a basic version for `decorators::time_it`. Recall, the
`time_it` decorator measures and displays the execution time of a function.

Step 1: Return the original function

```{r, echo=TRUE, eval=FALSE}
time_it <- function(func){
    return(func)
}
```

Step 2: Wrap the original function and return it (unmodified) 

```{r, echo=TRUE, eval=FALSE}
time_it <- function(func){
    
    wrapper <- function(...){
        return(func(...))
    }
    
    return(wrapper)
}
```

Step 3: Wrap the original function, modify it and return it

```{r, echo=TRUE, eval=TRUE}
time_it <- function(func){
    
    wrapper <- function(...){
        start_time <- Sys.time()
        
        result <- func(...)
        
        end_time <- Sys.time()
        
        print(difftime(end_time, start_time))
        
        return(result)
    }
    
    return(wrapper)
}
```

Finally, we demonstrate `time_it` by decorating the `sum` function

```{r, echo=TRUE, eval=TRUE}
## Before: sum() reports only the sum of its input
sum(1:3)

## Decorating sum with time_it 
sum <- time_it(base::sum)

## After: sum() reports both the sum of its input and the function's run time 
sum(1:3)
```
