---
title: "`purrr` Toolkit"
bibliography: [../../inst/REFERENCES.bib]
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```


<!-- The [`purrr`](https://purrr.tidyverse.org/reference) package provides a set of functions that allows -->

<!-- * Changing/setting default values of functions -->
<!-- * Handling unexpected conditions -->
<!-- * Altering the behaviour of a function -->

## Example: failproof `sum()`

The function `sum()` does one thing -- summing up a numeric vector.

```{r, echo=TRUE}
base::sum(1, 2, 3)
```

If the caller passes `sum()` non-numeric values then the function fails.

```{r, echo=TRUE, eval=FALSE}
base::sum(1, "2", 3)
```
```{r}
print('Error in base::sum(1, "2", 3) : invalid \'type\' (character) of argument')
```

Using `purrr::compose`, `purrr::safely`, and `purrr::pluck`, we can alternate
the behaviour of `sum()` to produce NA instead of failing:

```{r, echo=TRUE}
# Decorating `sum` with failproof mechanism:
# 1. Return NA when sum fails
# 2. Extract the result
sum <- purrr::safely(base::sum, otherwise = NA_real_)
sum <- purrr::compose(sum, ~ purrr::pluck(.x, "result"), .dir = "forward") 
```

With the decorated `sum()` function, the behaviour for non-numeric values alters

```{r, echo=TRUE}
sum(1, 2, 3)
sum(1, "2", 3)
```

The decorated `sum()` function is (a) failproof and (b) requires no changes in the codebase -- without it, a programmer would have encapsulated `sum()` instances with `tryCatch` statement
such as this:

```{r, echo=TRUE, eval=FALSE}
tryCatch(sum(x), error = function(e) return(NA_real_))
```

